Overview

### 2019-03-15 notebooks/general_info.Rmd
added scalar counting. 40% of arguments are just scalar

These are the updated counts.
```{r}
total_arguments <- apply_count_to_lopkg_c(los, args_count_all)
total_mono_type <- apply_count_to_lopkg_c(los, args_count_all_mono_type)
total_mono_attr <- apply_count_to_lopkg_c(los, args_count_all_mono_attr_pattern)
total_mono_clas <- apply_count_to_lopkg_c(los, args_count_all_mono_class)

total_functions <- apply_count_to_lopkg_c(los, length)
total_mono_type_functions <- apply_count_to_lopkg_c(los, fun_count_all_mono_type)
total_mono_attr_functions <- apply_count_to_lopkg_c(los, fun_count_all_mono_attr_pattern)
total_mono_clas_functions <- apply_count_to_lopkg_c(los, fun_count_all_mono_class)
```

@@

>>>>

These are the updated counts.
```{r}
# argument counts
total_arguments <- apply_count_to_lopkg_c(los, args_count_all)
total_mono_type <- apply_count_to_lopkg_c(los, args_count_all_mono_type)
total_mono_attr <- apply_count_to_lopkg_c(los, args_count_all_mono_attr_pattern)
total_mono_clas <- apply_count_to_lopkg_c(los, args_count_all_mono_class)
total_mono_all <- apply_count_to_lopkg_c(los, args_count_all_mono_all)
```

```{r}
# function counts
total_functions <- apply_count_to_lopkg_c(los, length)
total_mono_type_functions <- apply_count_to_lopkg_c(los, fun_count_all_mono_type)
total_mono_attr_functions <- apply_count_to_lopkg_c(los, fun_count_all_mono_attr_pattern)
total_mono_clas_functions <- apply_count_to_lopkg_c(los, fun_count_all_mono_class)
total_mono_all_functions <- apply_count_to_lopkg_c(los, fun_count_all_mono_all)
```

@@

How many things are just scalar?
```{r}
lo_scalars <- apply_row_extractor_to_lopkg_c(los, get_rows_from_df_only_scalar)
total_scalar_arguments <- apply_count_to_lopkg_c(lo_scalars, args_count_all)
```
